---
title: "End-of-life care: Services used and quality indicators"
author: "eilis.keeble@nuffieldtrust.org.uk"
date: "Created July 2023"
output:
  html_document:
    theme: null
    highlight: null
    mathjax: null
    toc: false
    fig_caption: false
    df_print: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

df <- arrow::read_feather(file = here::here("output", "os_reports", "input_os_reports.feather")) %>%
  mutate(dod_ons = as_date(dod_ons)
         , study_month = floor_date(dod_ons, unit = "month"))
```

**Produced using OpenSAFELY-TPP**

Created July 2023.

Last updated July 2023.

Updated 3-monthly, next update due XX.

This report extends on the analysis published [here](https://www.nuffieldtrust.org.uk/research/deaths-at-home-during-the-covid-19-pandemic-and-implications-for-patients-and-services).

## Index

1.  Background
2.  Deaths recorded in OpenSAFELY-TPP
3.  General practice interactions
  + Place of death
  + Cause of death
4.  Medications for symptom management

<br/><br/>

## Background

<br/><br/>

## Deaths recorded in OpenSAFELY-TPP

Draft text...

```{r create_table}
#read_csv("output/table.csv")
```

<br/><br/>

## General practice interactions

Draft text...

### Place of death

```{r create_chart_gp_place}
df %>%
  group_by(study_month) %>%
  summarise(count = n()) %>%
  ggplot() +
  geom_line(mapping = aes(x = study_month, y = count))
```

### Cause of death

<br/><br/>

## Medications for symptom management

<br/><br/>
